\documentclass[11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\begin{document}

\begin{center}
    {\LARGE \textbf{Loan Agreement Promissory Note (Texas)}}\\[1em]
    \textbf{\today}
\end{center}

\begin{flushleft}
    \textbf{David Bowie} \\
    \textbf{123ABC LLC.} \\
    \textbf{1 Hacker Way} \\
    \textbf{(Hereinafter referred to as the Borrower)} \\[1em]

    \textbf{Rick Gray} \\
    \textbf{7811 Iris Glen Ln., Richmond, TX 77407} \\
    \textbf{(Hereinafter referred to as the Lender)}
\end{flushleft}

\vspace{\baselineskip}

\noindent\textbf{1. Promise to Pay.}

For value received, the Borrower hereby unconditionally promises to pay to the order of
Lender the sum of \textbf{Ten Thousand Dollars (\$10,000)} together with interest accrued
at the rate of \textbf{10 percent (10\%)} per year on any unpaid balance on a
\textbf{FIXED 3 MONTH TERM}.

\vspace{\baselineskip}

\noindent\textbf{2. Origination Fee.}

Borrower agrees to pay Lender a one-time, non-refundable origination fee of
\textbf{Four Hundred Dollars (\$400)}, which shall be deducted and withheld by Lender
from the loan proceeds at the time of funding. Borrower acknowledges receipt of net
loan proceeds in the amount of \textbf{\$9,600.00}, representing the stated principal of
\textbf{\$10,000.00} less the origination fee. The origination fee compensates Lender for
administrative and processing costs and shall not be deemed or treated as interest for any
purpose, including usury calculations under applicable law.

\vspace{\baselineskip}

\noindent\textbf{3. Payable on Demand.}

The entire outstanding amount shall become immediately payable upon demand by the
Lender or holder of this Note, but demand shall not be made before the \textbf{12TH day of
FEBRUARY 2026}.

\vspace{\baselineskip}

\noindent\textbf{4. Place of Payment.}

Payment shall be made at the above stated address of the Lender or at such place as may
be designated from time to time in writing by the Lender or holder of this Note. For ease of
payment the Borrower may exercise the option to effect payment by direct deposit or
electronic transfer of funds into the account of Lender as specified in writing.

\vspace{\baselineskip}

\noindent\textbf{5. Prepayment.}

The Borrower may prepay this Note in full or in part at any time without premium or
penalty. All prepayments shall first be applied to accrued interest and thereafter to the
principal loan amount.

\vspace{\baselineskip}

\noindent\textbf{6. Default.}

Should the Borrower not make full payment within \textbf{10 days} of demand, this Note may be
turned over for collection and the Borrower agrees to pay all reasonable legal fees and
collection charges to the extent permissible by law, in addition to other amounts due.

\newpage

\noindent\textbf{7. Transfer.}

The Lender may transfer this Note to another holder without notice to the Borrower and the
Borrower agrees to remain bound to any subsequent holder of this Note under the terms of
this Note.

\vspace{\baselineskip}

\noindent\textbf{8. Replacement of Note.}

The Borrower agrees to execute a new Note with the same terms and conditions and
remaining value in the event that this Note is lost, stolen or mutilated. The Lender shall
release the Borrower of all obligations under the lost, stolen or mutilated Note in lieu of a
replacement new Note.

\vspace{\baselineskip}

\noindent\textbf{9. Joint and Several Liability.}

All Borrowers or Co-signors identified in this Note shall be equally liable for the repayment
of the debt described in this Note.

\vspace{\baselineskip}

\noindent\textbf{10. Borrower's Waiver.}

The Borrower waives presentment for payment, notice of non-payment, off-set, protest and
notice of protest and agrees to remain fully bound until this Note is paid in full.

\vspace{\baselineskip}

\noindent\textbf{11. Lender's Indulgence.}

No relaxation, indulgence, waiver, release or concession of any terms of this Note by the
Lender on one occasion shall be binding unless in writing and if granted shall not be
applicable to any other or future occasion.

\vspace{\baselineskip}

\noindent\textbf{12. Binding Effect.}

The terms of this Note shall be binding upon the Borrower's successors and shall accrue to
the benefit and be enforceable by the Lender and his/her successors, legal representatives
and assigns.

\vspace{\baselineskip}

\noindent\textbf{13. Jurisdiction.}

This Note shall be construed, interpreted and governed in accordance with the laws of the
State of Texas in case of any DEFAULT in repayment and should any provision of this Note
be judged by an appropriate court of law as invalid, it shall not affect any of the remaining
provisions whatsoever.

\vspace{\baselineskip}

\noindent\textbf{14. General.}

Where appropriate words signifying one gender shall include the others and words signifying
the singular shall include the plural and vice versa.

Paragraph headings are for convenience of reference only and are not intended to have any
effect in the interpretation or determining of rights or obligations under this Note.

\newpage

\noindent\textbf{Signed on this 12th day of November, 2025.}

\vspace{2\baselineskip}

\noindent
\begin{tabular}{@{} l l @{}}
\textbf{Borrower:} & \textbf{123ABC LLC.} \\[1.5cm]
\textbf{Signature:} & \textbf{\rule{6cm}{0.4pt}} \\
 & \textbf{David Bowie, Authorized Signatory} \\
\end{tabular}

\vspace{2\baselineskip}

\noindent
\begin{tabular}{@{} l l @{}}
\textbf{Lender:} & \textbf{Rick Gray} \\[1.5cm]
\textbf{Signature:} & \textbf{\rule{6cm}{0.4pt}} \\
\end{tabular}

\end{document}